Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2020-08-05 docs/00-manuscripts/ieee/ieee-manuscript.tex
incorportate Joses comments

\begin{equation}
	NRI_{i,j} = \frac{b_{i} - b_{j}}{b_{i} + b_{j}}
\end{equation}

\noindent
where \(i\) and \(j\) are the respective band numbers.

@@

Estimating feature importance for datasets with highly correlated features is a complicated task for which many different approaches, model-specific and agnostic, exist \cite{friedman2001, hastie2001, greenwell2018}..
The correlation between covariates makes it challenging to calculate an unbiased estimate for single features \cite{molnar2019}.
Methods like \ac{PDP} or permutation-based approaches may produce unreliable estimates in such scenarios because unrealistic situations between covariates are created \cite{molnar2019}.
The development of robust methods which enable an unbiased estimation of feature importance for highly correlated variables are subject to current research.

@@

% write about hyperspectral remote sensing
The field of (hyperspectral) remote sensing has a strong focus on using random forests for modeling in recent years \cite{belgiu2016}.
However, in high-dimensional scenarios, tuning parameter \texttt{\(m_{try}\)} becomes computationally expensive.
To account for this and the high dimensionality in general, studies used feature selection approaches like semi-supervised feature extraction \cite{xia2015}, wrapper methods \cite{fassnacht2014, feng2016, georganos2018}, PCA and adjusted feature selection \cite{rochac2016}.
However, no study that made use of filter methods in combination with hyperparameter tuning in the field of (hyperspectral) remote sensing could be found.
Potential reasons for this gap could be an easier access to wrappers methods and a higher general awareness of such compared to filter methods.
Applying the filter-based feature selection methodology shown in this study and its related code provided in the research compendium might be a helpful reference for future studies using hyperspectral remote sensing data.

@@

\section*{References}

@@

	He is a member of the International Max Planck Research School on Global Biogeochemical Cycles (IMPRS-gBGC, a joint program with the Max Planck Institute for Biogeochemistry.

>>>>

\begin{equation}
	NRI_{i,j} = \frac{band_{i} - band_{j}}{band_{i} + band_{j}}
\end{equation}

\noindent
with \(i\) and \(j\) being the respective band numbers.

@@

Estimating feature importance for datasets with highly correlated features is a complicated task for which many different approaches, model-specific and agnostic, exist \cite{friedman2001, hastie2001, greenwell2018}.
The correlation between covariates makes it challenging to calculate an unbiased estimate for single features \cite{molnar2019}.
Methods like \ac{PDP} or permutation-based approaches may produce unreliable estimates in such scenarios because unrealistic situations between covariates are created \cite{molnar2019}.
The development of robust methods which enable an unbiased estimation of feature importance for highly correlated variables are subject to current research.

@@

% write about hyperspectral remote sensing
The field of (hyperspectral) remote sensing has a strong focus on using random forests for modeling in recent years \cite{belgiu2016}.
However, in high-dimensional scenarios, tuning parameter \texttt{\(m_{try}\)} becomes computationally expensive.
To account for this and the high dimensionality in general, studies used feature selection approaches like semi-supervised feature extraction \cite{xia2015}, wrapper methods \cite{fassnacht2014, feng2016, georganos2018}, PCA and adjusted feature selection \cite{rochac2016}.
However, no study that made use of filter methods in combination with hyperparameter tuning in the field of (hyperspectral) remote sensing could be found.
Potential reasons for this gap could be an easier access to wrapper methods and a higher general awareness of such compared to filter methods.
Applying the filter-based feature selection methodology shown in this study and its related code provided in the research compendium might be a helpful reference for future studies using hyperspectral remote sensing data.

@@

@@

	He is a member of the International Max Planck Research School on Global Biogeochemical Cycles (IMPRS-gBGC), a joint program with the Max Planck Institute for Biogeochemistry.
